---
title: "Quiz"
author: "Wu Xingyi (Kyra)"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Questions
<br>

#### Question-7 Explain what is meant by local scope of a variable and illustrate it with an example code

**Solutions:** 

```{r, eval=T,echo=TRUE}
# Initialize x
x <- 5
sprintf("The value assigned to x outside the function is %d",x)

local <- function(x = 3) { 
return(x+3)
} 
local()

#Here, the value of x in the function is '3', and the code returns a value of "6" after adding "3" to x. 

sprintf("The final value of x globally after reassigning it to a different value inside the function remains as %d", x) #However, as you can see, the global value of x does not change. 
```
<br>

#### Question 8

Imagine you have a dataset containing information about customers and their purchases. The dataset is called "customer_purchases", and includes columns for "CustomerID" (type:dbl), "CustomerName" (type:chr), "PurchaseDate" (type:Date), and "PurchaseAmount" (type:dbl). Write a line of code for each of the following tasks

**Solutions:** 
a. Filter the dataset to include only purchases whose amount is greater than or equal to 100
```{r, eval=T,echo=TRUE}
library(dplyr)
filtered_data <- customer_purchases %>%
filter(PurchaseAmount >= 100)
```
b. List the filtered data in the decreasing order of their amount

```{r, eval=T,echo=TRUE}
sorted_data <- filtered_data %>%
arrange(desc(PurchaseAmount)) 

sorted_data()
```
<br>

#### Question-9 Download the titanic.csv Download titanic.csvfile into a folder on your computer, say “Quiz” inside your NM2207 folder, and
**Solutions:** 
a. Read the contents of the dataset (only code required)
```{r, eval=T,echo=TRUE}
library(readr)
titanic <- read_csv("titanic.csv")
```

b. List all the passengers who survived in class 3 (only code required)
```{r, eval=T,echo=TRUE}
survived_class3 <- titanic %>% 
  filter(Survived == 1, Pclass == 3)
```


c. Among those who survived in class 3, how many are female? (only code required)
```{r, eval=T,echo=TRUE}
female_survivors_class3 <- sum(survived_class3$Sex == "female")
female_survivors_class3
```
d. What is the mean value of the age of survivors in class 3? (only code required)
```{r, eval=T,echo=TRUE}
mean_age_survivors_class3 <- mean(survived_class3$Age, na.rm = TRUE)
mean_age_survivors_class3
```
e. List the survivors in class 3 in the decreasing order of their age (only code required)
```{r, eval=T,echo=TRUE}
survivors_class3_sorted <- survived_class3 %>% arrange(desc(Age))
survivors_class3_sorted
```
f. Obtain a plot of age of the survivors in class 3 versus their passenger id (only code required)
```{r, eval=T,echo=TRUE}
library(ggplot2)
ggplot(data=survived_class3, mapping=aes(x=Age,y=PassengerId)) + labs(x="Age",y="Passenger ID", title = "Age vs. Passenger ID") + geom_point(shape = 20, colour = "black", fill = "white", size = 1, stroke = 1)

```

#### Question-11 Evaluate the following code in RStudio and debug it. Explain what was wrong with the code, what the error-free code does and why the output of the function is different from carName?
```{r, eval=T,echo=TRUE}
carName <- 3

print_car_name <- function(){

names<-c("Volvo", "Mercedes", "Audi", "BMW")

carName<-names[carName]

return(carName)

}

cat("the name of the car you chose is", print_car_name(),", but the value of the variable carName is", carName)

```


**Solutions:** 

```{r, eval=T,echo=TRUE}
# Initialise a global variable, country_names, with the names of five countries of your choice
countryz_names <- c("India", "United States of AAAAAAAAAA", "United Kingdom", "Europe")

countryz_names

country_name_length <- function(countryz_names) {
  name_length <- nchar(countryz_names)
  long_names <- countryz_names[name_length > 8]
  longest_name <- max(long_names, na.rm = TRUE)
  print(paste("The longest name is", longest_name, "and its length is", nchar(longest_name)))
}


country_name_length(countryz_names)
print(name_length)
```




<br>
