---
title: "week 9 more like week i need some wine"
author: "Wu Xingyi (Kyra)"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Code along!

**lets go**

```{r, eval= T,echo= T}
library(tidyverse)
tidydata <- tribble(
~country,  ~year,  ~cases, ~population,
"Afghanistan", 1999,    745,   19987071,
"Afghanistan",  2000,   2666,   20595360,
"Brazil", 1999,  37737,  172006362,
"Brazil", 2000,  80488,  174504898,
"China",1999, 212258, 1272915272,
"China", 2000, 213766, 1280428583)

tidydata
```
#### next up!

**non tidy data**

```{r, eval= T,echo= T}
nontidydata <- tribble(
 ~country,~year,~rate,
 "Afghanistan",  1999, "745/19987071",
"Afghanistan",  2000, "2666/20595360",
"Brazil", 1999,  "37737/172006362",
"Brazil", 2000,  "80488/174504898",
"China",1999, "212258/1272915272",
"China", 2000, "213766/1280428583")

nontidydata
```

<br>

#### next up!

**non tidy data**

```{r, eval= T,echo= T}
nontidydata <- tribble(
 ~country,~year,~rate,
 "Afghanistan",  1999, "745/19987071",
"Afghanistan",  2000, "2666/20595360",
"Brazil", 1999,  "37737/172006362",
"Brazil", 2000,  "80488/174504898",
"China",1999, "212258/1272915272",
"China", 2000, "213766/1280428583")

nontidydata
```

<br>

#### tidying data

**non tidy examples**

```{r, eval= T,echo= T}
tidieddata <- nontidydata %>%
  separate(rate, into = c("cases",
                          "population"),
                            sep = "/")
tidieddata
```

<br>

#### new tidied data

**tidying more?**

```{r, eval= T,echo= T}
newtidieddata <- tidieddata %>%
  pivot_longer(
    cols = cases:population,
    names_to = "measurement",
    values_to = "value"
  )
newtidieddata
```

<br>

#### tidied data

**example 2**

```{r, eval= T,echo= T}
df <- tribble(
  ~id,  ~bp1, ~bp2,
   "A",  100,  120,
   "B",  140,  115,
   "C",  120,  125
) 
df

df %>%
  pivot_longer(
    cols = bp1:bp2,
    names_to = "measurement",
    values_to = "value"
)
```

<br>

#### tidied data

**example 3**

```{r, eval= T,echo= T}
newtidieddata

newtidieddata %>%
  pivot_wider(names_from="measurement",
              values_from="value")
```

<br>

#### tidied data

**example 4**

```{r, eval= T,echo= T}
df <- tribble(
  ~id, ~measurement, ~value,
  "A",        "bp1",    100,
  "B",        "bp1",    140,
  "B",        "bp2",    115,
  "A",        "bp2",    120,
  "A",        "bp3",    105
) 
df

df %>%
  pivot_wider(
    names_from = measurement,
    values_from = value
  )
```
<br>

#### scraping data from the web

**trying it out**

```{r, eval= T,echo= T}
#install.packages("rvest")
library(rvest)
webpage <- read_html("https://books.toscrape.com/")
table <-html_elements(webpage,"body")
```
<br>

**calling APIs**

```{r, eval= F,echo= T}
#install.packages(c("httr","jsonlite"))
library(jsonlite)
library(httr)

# current data
current_county_data_url <- "https://api.covidactnow.org/v2/counties.csv?apiKey=33382de96fd8441fb6c"
raw_data <- GET(current_county_data_url)
raw_data$status
raw_data$content

# historic data
historic_county_data_url <-
"https://api.covidactnow.org/v2/counties.timeseries.csv?apiKey=33382de96fd8441fb6c1eca82b3bd4ec"
raw_data <- GET(historic_county_data_url)
raw_data$status
raw_data$content

# individual location data
individual_loc_data_url <-
"https://api.covidactnow.org/v2/county/{49}.csv?apiKey=33382de96fd8441fb6c1eca82b3bd4ec"
raw_data <- GET(individual_loc_data_url)
raw_data$status
raw_data$content
```
<br>

## now for the challenge

<br>

#### loading

**the packages**

```{r, eval= T,echo= T}
library(tidyverse)
```

<br>

**Pivot longer to arrange the names of the columns, wk1 to wk76 under a new variable/column week (Hint use: cols = starts_with("wk") as the argument to pivot_longer() )**

```{r, eval= T,echo= T}
billboard_long <- billboard %>%
  pivot_longer(cols = starts_with("wk"), names_to = "week", values_to = "rank", values_drop_na = TRUE)

billboard_long
```

<br>


**Clean the "week" column to have only the week numbers (1 for wk1, 2 for wk2, etc.)**

```{r, eval= T,echo= T}
billboard_long <- billboard_long %>%
  mutate(week = parse_number(week))

billboard_long
```

<br>

**Plot the rank along the y-axis and week along the x-axis, joining the data points with 'geom_line()'**

```{r, eval= T,echo= T}
ggplot(billboard_long, aes(x = week, y = rank)) +
  geom_line() +
  labs(title = "Billboard Chart Rank Over Weeks", x = "Week", y = "Rank")

```

<br>

####  next question: loading

**the packages**

```{r, eval= T,echo= T}
library(tidyverse)
```

<br>

**Create as many columns as the distinct entries of the variable, measure_cd**

```{r, eval= T,echo= T}
pivot_wider(data = cms_patient_experience, 
            names_from = measure_cd, 
            values_from = prf_rate)
```

<br>

**Create as many columns as the distinct entries of the variable, measure_cd, the values in the columns should correspond to the ones listed in the column, prf_rate**

```{r, eval= T,echo= T}
pivot_wider(data = cms_patient_experience, 
            names_from = measure_cd, 
            values_from = prf_rate)
```

<br>

**The output doesn’t look quite right; we still seem to have multiple rows for each organization. That’s because, we also need to tell pivot_wider() which column or columns have values that uniquely identify each row; in this case those are the variables starting with "org"**

```{r, eval= T,echo= T}
pivot_wider(data = cms_patient_experience, 
            names_from = measure_cd, 
            values_from = prf_rate,
            id_cols = starts_with("org"))
```

<br>



