---
title: "Challenge-7"
author: "Wu Xingyi (Kyra)"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Uploading the Palmer Penguin Data

**Solutions:**

```{r, eval= T,echo=TRUE}
library(tidyverse) 
#install.packages("palmerpenguins")
library(palmerpenguins) 
glimpse(penguins)
```
<br>

#### Question-2: Plots: Palmer Penguins

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm,
                     colour = species)) +
  geom_point() +
  labs(title = "Bill depth and length",
subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguines",
       x = "Bill depth (mm)",
       y = "Bill length (mm)", colour = "Species", caption = "Source: Palmer tation LTER/ palmerpenguines package") + 
  scale_colour_viridis_d()
```
<br>

#### Question-3: Argument Names; Colour

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins) + aes(x = bill_depth_mm, y = bill_length_mm,
           colour = species) +
            geom_point() + scale_colour_viridis_d()
```
<br>

#### Question-4: Argument Names; Shape = Island

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
           shape = island)) +
  geom_point() + scale_colour_viridis_d()
```
<br>

#### Question-5:  Argument Names; Shape = Species

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
           shape = species)) +
  geom_point() + scale_colour_viridis_d()
```
<br>

#### Question-6: Argument Names; Size

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm,  y = bill_length_mm, colour = species, shape = species,
      size = body_mass_g)) +
  geom_point() + scale_colour_viridis_d()
```
<br>

#### Question-7: Alpha

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
      shape = species, size = body_mass_g, alpha = flipper_length_mm)) +
  geom_point() + scale_colour_viridis_d()
```
<br>

#### Question-8 Mapping

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins) +
  aes(x = bill_depth_mm,
      y = bill_length_mm,
      size = body_mass_g,
      alpha = flipper_length_mm) +
    geom_point()

```
<br>

#### Question-9: Setting

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins) +
  aes(x = bill_depth_mm,
      y = bill_length_mm) +
  geom_point(size = 2, alpha = 0.5)
```
<br>

#### Question-10: Faceting

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins) +
  aes(x = bill_depth_mm,
      y = bill_length_mm) +
  geom_point() +
  facet_grid(species ~ island)

```
<br>

#### Question-11: Faceting 2

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
  facet_grid(species ~ sex)

```
<br>

#### Question-12: Faceting 3

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
  facet_grid(sex ~ species)
```
<br>

#### Question-13:Faceting 4

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
  facet_wrap(~ species)
```
<br>

#### Question-14:Faceting 5

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
  facet_wrap(~ species, ncol = 2)
```
<br>

#### Question-15:Faceting 6

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
  facet_grid(. ~ species)
```
<br>

#### Question-16:Facet and Colour

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
  geom_point() + facet_grid(species ~ sex) + scale_color_viridis_d()
```
<br>

#### Question-17:Face and Colour, No Legend

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
  geom_point() + facet_grid(species ~ sex) + scale_color_viridis_d() +
  guides(color = "none")
```
<br>

#### Question-18: Uploading the Lending Club Data

**Solutions:** 

```{r, eval=T,echo=TRUE}
# install.packages("openintro")
library (openintro)
glimpse(loans_full_schema)
```
<br>

#### Question-19: Select Variables

**Solutions:** 

```{r, eval=T,echo=TRUE}
loans <- loans_full_schema %>%
  select(loan_amount, interest_rate, term, grade,
         state, annual_income, homeownership, debt_to_income)
glimpse(loans)

```
<br>

#### Question-20: Histograms 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans) + aes(x = loan_amount) +
  geom_histogram()
```
<br>

#### Question-21: Histograms and binwidth=1000 

**Solutions:** 

```{r, eval=T,echo=TRUE}
# binwidth = 1000
ggplot(loans, aes(x = loan_amount)) +
  geom_histogram(binwidth = 1000)
```
<br>

#### Question-22: Histograms and binwidth = 5000 

**Solutions:** 

```{r, eval=T,echo=TRUE}
# binwidth = 5000
ggplot(loans, aes(x = loan_amount)) +
  geom_histogram(binwidth = 5000)
```
<br>

#### Question-23: Histograms and binwidth=20000 

**Solutions:** 

```{r, eval=T,echo=TRUE}
# binwidth = 20000
ggplot(loans, aes(x = loan_amount)) +
  geom_histogram(binwidth = 20000)
```
<br>

#### Question-24: Customizing Histograms 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) + geom_histogram(binwidth = 5000) +
  labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club loans" )
```
<br>

#### Question-25: Fill with a categorical variable 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
  geom_histogram(binwidth = 5000, alpha = 0.5) +
labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans")
```
<br>

#### Question-26: Facet with a categorical variable 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) + geom_histogram(binwidth = 5000) +
  labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans") +
  facet_wrap(~ homeownership, nrow = 3)
```
<br>

#### Question-27: Density plot 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density()
```
<br>

#### Question-28: Density plots and adjusting bandwidth 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density(adjust = 0.5)
```
<br>

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) + geom_density(adjust = 1) # default bandwidth
```
<br>


```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density(adjust = 2)
```
<br>

#### Question-29: Customizing density plots 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density(adjust = 2) +
  labs( x = "Loan amount ($)", y = "Density", title = "Amounts of Lending Club loans" )
```
<br>

#### Question-30: Adding a categorical variable

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
  geom_density(adjust = 2, alpha = 0.5) +
  labs(x = "Loan amount ($)",y = "Density",title = "Amounts of Lending Club loans", fill = "Homeownership")
```
<br>

#### Question-31: Box plot 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = interest_rate)) +
  geom_boxplot()
```
<br>

#### Question-32: Box plot and outliers 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = annual_income)) +
  geom_boxplot()
```
<br>

#### Question-33: Customizing box plots 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = interest_rate)) +geom_boxplot() +labs(x = "Interest rate (%)",y = NULL,
    title = "Interest rates of Lending Club loans") +
  theme( axis.ticks.y = element_blank(), axis.text.y = element_blank() )
```
<br>

#### Question-34: Adding a categoric variable 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = interest_rate,
y = grade)) +
  geom_boxplot() +
  labs(x = "Interest rate (%)",y = "Grade",title = "Interest rates of Lending Club loans",subtitle = "by grade of loan")
```
<br>

#### Question-35: Scatterplot 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
  geom_point()
```
<br>

#### Question-36: Hex Plot 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans %>% filter(debt_to_income < 100),
       aes(x = debt_to_income, y = interest_rate)) +
geom_hex()
```
<br>

#### Question-37: Bar Plot 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = homeownership)) +
  geom_bar()
```
<br>

#### Question-38: Segmented Bar Plot 

**Solutions:** 
```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = homeownership,
                  fill = grade)) +
geom_bar()
```

<br>

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = homeownership,
                  fill = grade)) +
geom_bar(position = "fill")
```
<br>

#### Question-39: Customizing bar plots 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(y = homeownership, fill = grade)) + geom_bar(position = "fill") +
labs( x = "Proportion", y = "Homeownership", fill = "Grade", title = "Grades of Lending Club loans")
```
<br>

#### Question-40: Violin Plots 

**Solutions:** 

```{r, eval=T,echo=TRUE}
ggplot(loans, aes(x = homeownership, y = loan_amount)) +
  geom_violin()
```
<br>

#### Question-41: Ridge Plots 

**Solutions:** 

```{r, eval=T,echo=TRUE}
#install.packages("ggridges")
library(ggridges)
ggplot(loans, aes(x = loan_amount, y = grade, fill = grade, color = grade)) +
  geom_density_ridges(alpha = 0.5)
```
<br>







