---
title: "Final Project Submission"
author: "Wu Xingyi (Kyra)"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Week 13: Final Submission

## What is the theme of your data story?

In this project, I delved into McDonald's global narrative, exploring
its influence on diverse cultures and economies. Intrigued by its
ubiquitous presence and global symbolism, I examined McDonald's through
cultural, nutritional, and economic lenses. The project unfolds in
layers, starting globally and eventually narrowing down:

1.   **Global Perspective (Where to Eat McDonald's):\
    **Utilizing **mcdonalds.R**, I crafted an interactive global map to
    showcase McDonald's widespread presence. This visual tool revealed
    the scale of the chain worldwide, highlighting regions with high
    concentrations and limited presence. This macro-level view was
    instrumental in understanding McDonald's as a global cultural
    phenomenon.

2.  **Economic Perspective (When to Order McDonald's):**

    In **bigmacprice.R**, I focused on a localized, temporal, economic
    view by analysing the Big Mac Index. Users could explore variations
    in Big Mac prices across regions, gaining insights into economic
    aspects like local purchasing power and currency valuation. This
    economic analysis provided a practical guide to the affordability of
    McDonald's in different regions.

    **3.	Individual Perspective (What to Order at McDonald's):**

    Using **McDCorrelation.R** and **McDNutrition.R,** I analysed the
    nutritional content of McDonald's menu items. This allowed users to
    make informed choices based on nutritional value. The correlation
    analysis provided insights into how different nutritional elements
    were interrelated, aiding users in making healthier or more balanced
    food choices at McDonald's.

## Why is it important to address this question?

Investigating McDonald's is crucial for several reasons as it connects
to several real world topics.

1.  **Cultural Globalization and Adaptation**: McDonald's exemplifies
    cultural globalization, showcasing the global influence of American
    culture. While spreading worldwide, the chain also adapts to local
    cultures, evident in regional menu variations (Racoma, 2019). This
    aspect raises questions about cultural identity, globalization, and
    the balance between a global brand and local preferences.

2.  **Economic Changes:** The project explores the changes in Big Mac
    prices across subregions, examining how McDonald's adapts its
    pricing strategies to diverse economic environments. By focusing on
    these adjustments, the research provides insights into the global
    economic dynamics influencing consumer behaviour and multinational
    corporations like McDonald's.

3.  **Global Health and Nutrition**: Addressing the pressing issue of
    global health and nutrition, the project focuses on McDonald's, a
    major player in the fast-food industry (Alliance for a Healthier
    Generation, 2013). This research aids discussions on healthier food
    choices and the role of fast-food chains in promoting a balanced
    diet.

## Why do you think the data sources that you have curated can help you answer the question?

The data sources I curated are ideal for this analysis. The data on
McDonald's locations per country helps in visualizing the chain's global
reach and density, indicating cultural penetration and market dominance.
The Big Mac price data set provides a lens into economic aspects,
particularly in comparing cost of living across countries. The
McDonald's nutritional information data set allows for an in-depth
examination of the nutritional value of menu items, crucial for
understanding health implications. Lastly, the McDonald's menu data set
offers insights into product diversity and localization strategies.

1.  [Most McDonald's Locations Per
    Country](https://openaxis.com/data/3740) (Factle App, 2022)

2.  [Big Mac
    Price](https://www.kaggle.com/datasets/vittoriogiatti/bigmacprice/data)
    (Giatti, 2022)

3.  [McDonald's Nutrition
    Facts](https://www.kaggle.com/datasets/mcdonalds/nutrition-facts)
    (McDonald\'s, 2016)

4.  [McDonald's
    Menu](https://github.com/schmwong/APAC-McDelivery-Menu-Logger)
    (Wong, 2022/2023)

## What are the insights from the data and how are they depicted in plots?

**Global Presence and Cultural Reach**: The interactive maps I developed
in **mcdonalds.R** using leaflet were instrumental in showing how
extensively McDonald's has penetrated different markets. This
visualization brought to light patterns of globalization and market
saturation.

**Economic Insights from Big Mac Prices**: In **bigmacprice.R**, I
employed **ggplot2** to illustrate the variation in Big Mac prices
globally. This not only provided a practical example of purchasing power
parity but also hinted at economic disparities between countries.

**Correlation Analysis**: With **McDCorrelation.R**, I was able to
visually represent the relationships between various nutritional
components of McDonald's menu items. This helped in identifying
potential health impacts of different food choices.

**Nutritional Analysis**: Using **McDNutrition.R**, I created plots that
highlighted the caloric density, fat content, and other nutritional
aspects of various menu items. The **corrplot** visualization showed
interesting correlations, like the link between calories and fat
content, which were critical for understanding the nutritional profile
of McDonald's offerings.

## How did you implement this entire project? Were there any new concepts that you learnt to implement some aspects of it?

This project encompassed various aspects of data science, including data
collection, cleaning, analysis, and visualization. I honed my R skills,
focusing on packages like **tidyverse**, **ggplot2**, and **plotly** for
data manipulation and creating meaningful visualizations.

In **McDNutrition.R**, I delved into text mining, extracting and
analyzing words from McDonald's menu items, exploring linguistic
patterns and trends. **McDCorrelation.R** deepened my grasp of
statistical relationships within the data, which was essential for
drawing meaningful conclusions about McDonald's nutritional offerings.

Reflecting on my journey, I encountered challenges as a newcomer to R:

1.  **Data Cleaning and Preparation**: Initially, preparing datasets for
    analysis posed challenges, involving mastering tidyverse functions
    like **mutate**, **filter**,and **select**. Significant cleaning and
    manipulation of nutritional and global location data were necessary,
    addressing issues such as missing values, inconsistent formats, and
    merging data from diverse sources.

2.  **Interactive App Development with Shiny**

    -   [*Building*]{.underline}: Creating interactive web applications
        with Shiny was challenging, requiring comprehension of both R
        backend and UI design. Managing user inputs, reactive outputs,
        and ensuring app performance posed challenges, especially as a
        beginner handling both server and UI aspects.

    -   [*Deployment Issues*]{.underline}: Deploying the app to Shiny.io
        initially faced hurdles, encountering errors post-upload.
        Understanding differences between local and server environments,
        including package versions and data access, was crucial.

    -   *Debugging Remote Errors*: Debugging on Shiny.io proved more
        complex than local debugging. Interpreting Shiny.io error logs
        and tracing issues back to specific code sections demanded
        attention, but it was essential for effective issue resolution.

3.  **Complexity of Data Visualization**: Creating effective
    visualizations with **ggplot2** and **plotly** was a steep learning
    curve for a beginner like me. Understanding syntax, experimenting
    with plot types, customizing themes, and ensuring clarity in data
    representation were vital. Extensive online searches were necessary
    to discover and utilize specific packages.

4.  **Statistical Analysis and Interpretation**: The project involved
    substantial statistical analysis, especially with the
    **McDCorrelation.R** script. Grasping concepts like correlation and
    interpreting them correctly in the context of McDonald's nutritional
    data demanded not only technical R skills but also a foundational
    understanding of statistics.

In summary, this project provided an enriching learning journey,
applying various data science techniques to a real-world scenario. It
offered valuable insights into a globally recognized brand, honing
analytical skills, and expanding understanding of how data uncovers
stories and trends shaping our world.

## *References*

Alliance for a Healthier Generation. (2013, September 26). *Alliance and
McDonald\'s Announce Groundbreaking CGI Commitment to Promote Balanced
Food and Beverage Choices* [Text].
[https://www.healthiergeneration.org/articles/alliance-and-mcdonalds-announce-groundbreaking-cgi-commitment-to-promote-balanced-food](https://www.healthiergeneration.org/articles/alliance-and-mcdonalds-announce-groundbreaking-cgi-commitment-to-promote-balanced-food-and)

Racoma, B. (2019, January 4). *McDonald\'s International Strategy:
Adapting Around the World*. Day Translations Blog.
<https://www.daytranslations.com/blog/mcdonalds-international-strategy-adapting-around-the-world/>

## *Data Sources*

Factle App. (2022, May 15). *Most McDonald\'s locations per country (as
of 2022)*. <https://openaxis.com/data/3740>

Giatti, V. (2022). *Bigmac Prices*.
<https://www.kaggle.com/datasets/vittoriogiatti/bigmacprice>

McDonald\'s. (2016). *Nutrition Facts for McDonald\'s Menu*.
<https://www.kaggle.com/datasets/mcdonalds/nutrition-facts>

Wong, P. (2023). *McDelivery Menu Logger (APAC Region)* [Python].
<https://github.com/schmwong/APAC-McDelivery-Menu-Logger> (Original work
published 2022)

*1178 Words*

# Week 12

## Challenges Faced

The biggest challenge I faced this week was deploying my shiny app, and
then trying to get the actual diagram to be interactive. Cleaning the
data was also ridiculously hard. I want to make interactive maps but my
country data is in the wrong format so I had to some how insert that
kind of data as well... Another is the fact that alot of the graphs I am
trying to do, I do not really know how to implement them on Shiny.
Furthermore, trying to string all the diagrams together to form one
cohesive story was also very challenging. Making the final website
pretty would be one of the last problems I forsee myself facing.

# Week 11

### List the visualizations that you are going to use in your project (Answer: What are the variables that you are going to plot? How will it answer your larger question?)

Nutritional Value Comparison: I will create bar charts or radar charts
to compare the nutritional content between different menu items

This visualization will help answer the question of how the average
price of McDonald's menu items varies across different countries or
regions. It can reveal insights into economic disparities, currency
exchange rates, and local market factors that influence pricing.

Perhaps, another visualization that showcases the average price of
McDonald's menu items across various countries, using a world map
color-coded by price ranges to provide a quick overview of pricing
disparities.

I also plan to create a visualization that combines Big Mac prices with
the number of people per outlet at McDonald's locations to identify the
cheapest and most accessible places to eat. To do this, I'm considering
two types of visualizations: *Geographical Scatterplot*: I'll use a
scatterplot where the x-axis will show the number of people served by
each outlet, and the y-axis will display the Big Mac price at that
location. Each point's color will indicate the price range or
accessibility level; for example, green for affordable and accessible
and red for expensive and less accessible outlets. The size of the
points could represent the popularity of each outlet.

*Heatmap*: Another option is to create a heatmap that showcases regions
or areas using different shades of color. The intensity of the color
will reflect a combination of the Big Mac price and the number of people
served per outlet. Darker shades on the map could signify cheaper and
more accessible areas, while lighter shades could indicate pricier and
less accessible locations.

### How do you plan to make it interactive? (Answer: features of ggplot2/shiny/markdown do you plan to use to make the story interactive)

Inputs: Use Shiny's input functions like selectInput(), sliderInput(),
and textInput() to allow users to filter or customize the data displayed
in the visualizations. For example, create a dropdown menu for selecting
regions or a slider for choosing a price range.

Tooltips: Integrate tooltips using Shiny's hoverText() or hoverInfo() to
display additional information when users hover over data points in the
visualizations. This can include specific price values, number of people
served, or other relevant data.

Linked Visualizations: [This one might be harder] Use Shiny's linking
feature to establish interactivity between different plots. When a user
interacts with one plot (e.g., selecting a region), it can update or
filter data in other linked plots, providing a more holistic view of the
data.

ggiraph Package: I am also considering using the ggiraph package, which
extends ggplot2 to create interactive graphics. This can include
interactive bar charts, scatterplots, or other visualizations where
users can click on elements for more information.

### What concepts incorporated in your project were taught in the course and which ones were self-learnt? (Answer: Create a table with topics in one column and Weeks in the other to indicate which concept taught in which week is being used. Leave the entry of the Week column empty for self-learnt concepts)

```{r}
library(knitr)
concepts_table <- data.frame(
  Topics = c(
    "Data Visualization with ggplot2",
    "Interactive Web Applications with Shiny",
    "Markdown for Document Creation",
    "Data Cleaning and Pre-processing",
    "Exploratory Data Analysis",
    "Data Filtering and Transformation",
    "Statistical Analysis and Plotting",
    "Linking Visualizations in Shiny",
    "Embedding Shiny Widgets in R Markdown"
  ),
  Weeks = c(
    "Week 2 & 7",
    "Week 2",
    "Week 1",
    "Week 4",
    "Week 9 + Self Learned",
    "Week 4 + Self Learned",
    "Week 7",
    "Self Learned",
    "Announcements: Integration of Shiny dashboard with Quarto"
  )
)

kable(concepts_table, format = "markdown")
```

# Week 10

### What is the question that you are going to answer? (Answer: One sentence that ends with a question mark that could act like the title of your data story)

What should you order next at Mcdonalds? (Depending on Nutritional Value
and Price)

### Why is this an important question? (Answer: 3 sentences, each of which has some evidence, e.g., "According to the United Nations..." to justify why the question you have chosen is important)

This question is important because McDonald's is one of the most popular
fast food restaurants in the world, and many people are looking for ways
to make healthier choices when eating there. Additionally, many people
are on a budget, and want to get the most value for their money.

[**https://edition.cnn.com/2018/10/03/health/fast-food-consumption-cdc-study/index.html**](https://edition.cnn.com/2018/10/03/health/fast-food-consumption-cdc-study/index.html){.uri}

A study by The Journal of Preventive Medicine and Hygiene (JPMH) found
that people who eat fast food more than twice a week are more likely to
be overweight or obese. Additionally, fast food is often high in
unhealthy fats, sugar, and sodium.

[**https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6196377/**](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6196377/){.uri}

Lastly, cost is a crucial factor for many consumers, especially those on
tight budgets. Understanding the trade-off between nutrition and price
at a popular fast-food restaurant like McDonald's can help individuals
and families make more informed decisions when dining out, contributing
to financial well-being. Addressing this question can ultimately promote
healthier eating habits while keeping affordability in mind.
[**https://egrove.olemiss.edu/cgi/viewcontent.cgi?article=1593&context=etd**](https://egrove.olemiss.edu/cgi/viewcontent.cgi?article=1593&context=etd){.uri}

# **Data**

### Which rows and columns of the dataset will be used to answer this question? (Answer: Actual names of the variables in the dataset that you plan to use).

#### Big Mac (Ala Carte) in APAC (Row), Territory (Column) - <https://github.com/schmwong/APAC-McDelivery-Menu-Logger>

#### Category, Item, Calories, Total Fat, Saturated Fat, Trans Fat - <https://www.kaggle.com/datasets/mcdonalds/nutrition-facts>

#### Country, Number of Restaurants, Number of Restaurants per Million Population - <https://openaxis.com/data/3740>

### Challenges: The sheer volume of data sets can be overwhelming. It becomes difficult to manage and analyze them comprehensively, especially if they are diverse in terms of format, structure, or content.With numerous data sets, I often find myself losing sight of the main narrative or research question. This can lead to a lack of clarity and direction in my analysis, making it challenging to derive meaningful insights. Furthermore, they might not naturally intersect or provide a clear link to build a cohesive narrative. Finding the connections between these sets can be time-consuming and demanding.

# Week 9

## What Is The Topic That You Have Finalized?

The topic I have finalized for my project is an in-depth analysis of
McDonald's meals, with a specific focus on their nutritional content,
pricing, and the geographical distribution of McDonald's stores. This
research aims to examine the nutritional value of popular menu items,
such as Big Macs, and how their prices vary across different locations,
providing insights into the relationship between menu offerings,
nutrition, and cost-effectiveness.

## What Are The Data Sources That You Have Curated So Far?

### Nutrition Facts for McDonald's Menu

<br> <https://www.kaggle.com/datasets/mcdonalds/nutrition-facts>

### Big Mac Prices

<br> <https://www.kaggle.com/datasets/vittoriogiatti/bigmacprice/data>

### APAC-McDelivery-Menu-Logger

<br> <https://github.com/schmwong/APAC-McDelivery-Menu-Logger>

### Data-mcdonalds-nutrition

<br>
<https://github.com/tsterbak/data-mcdonalds-nutritionfacts/blob/master/workbooks/pffy-data-mcdonalds-nutrition-facts.xlsx>

```{r}
library(shiny)
library(readr)
library(ggplot2)
library(rnaturalearth)
library(tidyverse)

ui <- fluidPage(
  tags$head(
    tags$style(HTML("
      body {background-color: #f7f7f7;} 
      .well {background-color: #ffffff; border-radius: 8px; box-shadow: 0 4px 8px 0 rgba(0,0,0,0.2);} 
      .shiny-input-container {padding: 10px;} 
      .selectize-input {border-radius: 4px; border: 1px solid #ced4da; height: calc(2.25rem + 2px);} 
      .selectize-dropdown {border-radius: 4px; border: 1px solid #ced4da;}
      .btn {background-color: #007bff; color: white; border-radius: 4px;} 
      .btn:hover {background-color: #0056b3;}
      #bigMacTimeSeries {border-radius: 8px; overflow: hidden; background-color: #CBC3E3;}
    "))
  ),
  
  fluidRow(
    column(12, 
           div(plotOutput("bigMacTimeSeries"), style = "border-radius: 8px; overflow: hidden;")
    )
  ),
  fluidRow(
    column(12, 
           wellPanel(
             selectInput("grouping", "Select Grouping:",
                         choices = c("Continent" = "continent",
                                     "Subregion" = "subregion",
                                     "Economy" = "economy",
                                     "Income Group" = "income_grp")),
             checkboxInput("showAnnotations", "Show Annotations", TRUE)
           )
    )
  )
)


server <- function(input, output, session) {
  bigMacData <- read_csv("BigmacPrice.csv") %>%
    mutate(name = case_when(
      name == "Hong Kong" ~ "Hong Kong S.A.R.",
      name == "Britain" ~ "United Kingdom",
      name == "UAE" ~ "United Arab Emirates",
      name == "United States" ~ "United States of America",
      TRUE ~ name
    ))
  world_countries <- ne_countries(scale = "medium", returnclass = "sf")
  bigMacData <- bigMacData %>%
    left_join(world_countries, by = c("name" = "admin")) %>% 
    select("name","date", "dollar_price", "continent", "subregion",
           "pop_est", "gdp_md_est", "economy", "income_grp") 
  
  #avg by continent
  averagePriceByContinent <- bigMacData %>%
    group_by(continent, date) %>%
    summarize(average_dollar_price = mean(dollar_price, na.rm = TRUE)) %>%
    ungroup()  
  #avg by subregion
  averagePriceBysubregion <- bigMacData %>%
    group_by(subregion, date) %>%
    summarize(average_dollar_price = mean(dollar_price, na.rm = TRUE)) %>%
    ungroup()  
  #avg by economy
  averagePriceByeconomy <- bigMacData %>%
    group_by(economy, date) %>%
    summarize(average_dollar_price = mean(dollar_price, na.rm = TRUE)) %>%
    ungroup()  
  #avg by economy
  averagePriceByincome <- bigMacData %>%
    group_by(income_grp, date) %>%
    summarize(average_dollar_price = mean(dollar_price, na.rm = TRUE)) %>%
    ungroup()  
  
  selectedData <- reactive({
    switch(input$grouping,
           "continent" = averagePriceByContinent,
           "subregion" = averagePriceBysubregion,
           "economy" = averagePriceByeconomy,
           "income_grp" = averagePriceByincome)
  })
  
  output$bigMacTimeSeries <- renderPlot({
    
    p <- ggplot(selectedData(), aes_string(x = "date", y = "average_dollar_price", group = input$grouping, color = input$grouping)) +
      geom_line() +
      theme_minimal() +
      labs(title = "Big Mac Index Over Time", x = "Date", y = "Price (Local Currency)") + 
      scale_color_brewer(palette = "Set2") +
      theme(panel.background = element_rect(fill = "#F5F5F5")) 
    
    if (input$showAnnotations) {
      p <- p + 
        geom_vline(xintercept = as.Date("2003-09-02"), linetype = "dashed", color = "#ffc10B") +
        geom_vline(xintercept = as.Date("2004-07-08"), linetype = "dashed", color = "red") +
        geom_rect(aes(xmin = as.Date("2007-12-01"), xmax = as.Date("2009-06-30"), ymin = -Inf, ymax = Inf), fill = "red", alpha = 0.002) +
        geom_rect(aes(xmin = as.Date("2020-03-01"), xmax = as.Date("2020-06-30"), ymin = -Inf, ymax = Inf), fill = "red", alpha = 0.002) +
        annotate("text", x = as.Date("2003-09-02"), y = Inf, label = "I'm Lovin' It launch", vjust = 2, color = "#ffc10b", fontface = "bold") +
        annotate("text", x = as.Date("2004-07-08"), y = Inf, label = "Super Size Me Documentary", vjust = 5, color = "red", fontface = "bold") +
        annotate("text", x = as.Date("2007-12-01"), y = Inf, label = "Global Financial Crisis", vjust = 7, color = "red", fontface = "bold") +
        annotate("text", x = as.Date("2020-03-01"), y = Inf, label = "COVID Lockdown", vjust = , color = "red", fontface = "bold")
    }
    p
  })
}

shinyApp(ui, server)
```
