---
title: "Challenge-5"
author: "Wu Xingyi (Kyra)"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
x <- 5
sprintf("The value assigned to x outside the function is %d",x)

inside_function <- function() {
  x <- 10
  message(sprintf("The value of x inside the function is %d", x))
}
sprintf("The value assigned to x outside the function is %d",x)
inside_function()

```
<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
total <- 0

accumulated_total <- function(value) {
  total <<- total + value
}

accumulated_total(5)
accumulated_total(10)
accumulated_total(7)

print(sprintf("Total: %d", total))
```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Interpreted this question's "updated total" differently from the previous questions 
# "accumulated total" where we had to change the value of the global total versus 
# just adding numbers on a one-time basis to the total. 
total <- 100

updated_total <- function(val) {
  return(total + val)
}

updated_total(1)
updated_total(10)
updated_total(100)

```
<br>

#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
outer_function = function() {
  x = 5
  inner_function = function() {
    print(x)
  }
  inner_function()
}

outer_function()
```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
#install.packages("magick")
library(magick)

meme = function(text) {
  frink <- image_read("https://jeroen.github.io/images/frink.png")
  frink <- image_border(image_background(frink, "hotpink"), "#000080", "20x10")
  frink <- image_negate(frink)
  frink <- image_annotate(frink, text = text, size = 25, color = "red", boxcolor = "pink",
    degrees = 30, location = "+60+70")
  print(frink)
}

meme("me on mondays")
```
<br>



#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user inputs a sentence, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Unfortunately, the TA and I were unable to figure out how to make the knitted PDF  
# interactive to allow for user input :< 
analyze_text <- function(sentence) {
  words <- unlist(strsplit(sentence, " "))
  num_words <- length(words)
  num_chars <- nchar(sentence)
  skill_level <- ifelse(num_words <= 5, "Beginner",
                        ifelse(num_words <= 10, "Intermediate", 
                               ifelse(num_words <= 15, "Advanced")))

  summary <- paste(
    "Number of Words:", num_words,
    "\nNumber of Characters:", num_chars,
    "\nCommunication Skill Level:", skill_level
  )
  
  return(summary)
}

sentence <- readline(prompt = "Enter a sentence to analyze: ")

analysis_result <- analyze_text(sentence)

cat("\nAnalysis Result:\n")
cat(analysis_result,"\n")
```
<br>